\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-04-28 write_up/mixfishsim_ecolmod.tex
Text update

For the commercial data, the most effective closure scenario was based on 1 x 1
data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
in F for species 1. \textcolor{blue}{This was the only closure scenario to have
	positive effect according to Figure \ref{fig:4}, though looking at the
	trend in Figure \ref{fig:3} this looks more related to the continued
	increased in F trend, as other scenarios had an initial effect}.
Interestingly the monthly data scenario was more effective than weekly data,
which I'd posit is due to the increase amount of data available from the
commercial sampling across a month compared to a week.i Commercial data used at
an annual time-step was ineffective in bringing fishing mortality down for
species 1. \\

@@

Our study evaluates the importance of data scaling and considers potential
biases introduced through data aggregation when using commercial fisheries
logbooks and Vessel Monitoring Systems for inference on spatio-temporal
dynamics in fisheries. Understanding how fishers exploit multiple
heterogeneously distributed fish populations with different catch limits or
conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to the patchy and irregular nature of fisheries resulting in preferential
sampling \cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated
which requires assumptions about the spatial and temporal scale of processes.
Our study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\cite{Dunn2016}, understanding assumptions behind the data used is vital to
ensure measures are effective. \\

>>>>

For the commercial data, the most effective closure scenario was based on 1 x 1
data at a monthly temporal resolution. This results in $\sim$ 10 \% reduction
in F for species 1. \textcolor{blue}{This was the only closure scenario to have
	positive effect according to Figure \ref{fig:4}, though looking at the
	trend in Figure \ref{fig:3} this looks more related to the continued
	increased in F trend, as other scenarios had an initial effect}.
Interestingly the monthly data scenario was more effective than weekly data,
which I'd posit is due to the increase amount of data available from the
commercial sampling across a month compared to a week. Commercial data used at
an annual time-step was ineffective in bringing fishing mortality down for
species 1. \\

@@

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using commercial fisheries data to
infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes.  Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\cite{Dunn2016}, understanding assumptions behind the data used - increasingly
a combination of logbook and positional information from vessel monitoring
systems - is vital to ensure measures are effective. \\
